Replacing standard galaxy profiles with \\ mixtures of Gaussians

### 2012-10-23 documents/mixtures/mixture_models.tex
use pdfs for figures

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile.png}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{exp_K06_MR08_residual.png}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_fractional_log.png}
\caption{\textsl{top-left:} The true exp profile (thin black line),
  the best $M^{\exp}=6$ mixture-of-Gaussian approximation (thick grey
  line), and the component Gaussians (multiplied by their
  corresponding amplitudes) contributing to the approximation (thin
  grey lines).  The plot title text gives $\xi_{\max}$ and the
  badness. \textsl{top-right:} The same but shown logarithmically.
  \textsl{bottom-left:} A representation of the residual or devation,
  on which the badness is computed.  \textsl{bottom-right:} The same
  but shown fractionally and logarithmically.\label{fig:exp}}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual.png}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_fractional_log.png}
\caption{The dev profile and the best $M^{\dev}=10$ approximation.
  The panels are equivalent to those in \figurename~\ref{fig:exp}.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{lux_K06_MR04_profile.png}%
\includegraphics[width=\figurewidth]{lux_K06_MR04_profile_log.png}\\
\includegraphics[width=\figurewidth]{luv_K08_MR08_profile.png}%
\includegraphics[width=\figurewidth]{luv_K08_MR08_profile_log.png}
\caption{The lux and luv profiles and approximations.  The panels are
  equivalent to those in the top-row of \figurename~\ref{fig:exp}.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{ser2_K10_MR08_profile_log.png}%
\includegraphics[width=\figurewidth]{ser3_K10_MR08_profile_log.png}\\
\includegraphics[width=\figurewidth]{ser5_K10_MR08_profile_log.png}%
\includegraphics[width=\figurewidth]{mixtures_vs_model_K10.png}
\caption{Three ser profiles---with $n=2$, $3$, and $5$---and
  approximations.  The top-left, top-right, and bottom-left panels are
  equivalent to those in the top-right of \figurename~\ref{fig:exp}.
  \textsl{bottom-right:} The dependence on the amplitudes $a^{\ser}_m$
  and root-variances $\sqrt{v^{\ser}_m}$ on ser index $n$.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{mixtures_vs_K_exp.png}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_dev.png}\\
\includegraphics[width=\figurewidth]{mixtures_vs_K_lux.png}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_luv.png}
\caption{Comparisons of approximations.  \textsl{top-left:} The
  dependence of amplitude $a^{\exp}_m$ and root-variance
  $\sqrt{v^{\exp}_m}$ on $M^{\exp}$ for the exp profile.
  \textsl{top-right:} The same but for the dev profile.
  \textsl{bottom-left:} The same but for the lux profile.
  \textsl{bottom-right:} The same but for the luv profile.\label{fig:M}}
\end{figure}

>>>>

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile.pdf}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_profile_log.pdf}\\
\includegraphics[width=\figurewidth]{exp_K06_MR08_residual.pdf}%
\includegraphics[width=\figurewidth]{exp_K06_MR08_fractional_log.pdf}
\caption{\textsl{top-left:} The true exp profile (thin black line),
  the best $M^{\exp}=6$ mixture-of-Gaussian approximation (thick grey
  line), and the component Gaussians (multiplied by their
  corresponding amplitudes) contributing to the approximation (thin
  grey lines).  The plot title text gives $\xi_{\max}$ and the
  badness. \textsl{top-right:} The same but shown logarithmically.
  \textsl{bottom-left:} A representation of the residual or devation,
  on which the badness is computed.  \textsl{bottom-right:} The same
  but shown fractionally and logarithmically.\label{fig:exp}}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile.pdf}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_profile_log.pdf}\\
\includegraphics[width=\figurewidth]{dev_K10_MR08_residual.pdf}%
\includegraphics[width=\figurewidth]{dev_K10_MR08_fractional_log.pdf}
\caption{The dev profile and the best $M^{\dev}=10$ approximation.
  The panels are equivalent to those in \figurename~\ref{fig:exp}.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{lux_K06_MR04_profile.pdf}%
\includegraphics[width=\figurewidth]{lux_K06_MR04_profile_log.pdf}\\
\includegraphics[width=\figurewidth]{luv_K08_MR08_profile.pdf}%
\includegraphics[width=\figurewidth]{luv_K08_MR08_profile_log.pdf}
\caption{The lux and luv profiles and approximations.  The panels are
  equivalent to those in the top-row of \figurename~\ref{fig:exp}.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{ser2_K10_MR08_profile_log.pdf}%
\includegraphics[width=\figurewidth]{ser3_K10_MR08_profile_log.pdf}\\
\includegraphics[width=\figurewidth]{ser5_K10_MR08_profile_log.pdf}%
\includegraphics[width=\figurewidth]{mixtures_vs_model_K10.pdf}
\caption{Three ser profiles---with $n=2$, $3$, and $5$---and
  approximations.  The top-left, top-right, and bottom-left panels are
  equivalent to those in the top-right of \figurename~\ref{fig:exp}.
  \textsl{bottom-right:} The dependence on the amplitudes $a^{\ser}_m$
  and root-variances $\sqrt{v^{\ser}_m}$ on ser index $n$.}
\end{figure}

\clearpage
\begin{figure}
\includegraphics[width=\figurewidth]{mixtures_vs_K_exp}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_dev}\\
\includegraphics[width=\figurewidth]{mixtures_vs_K_lux}%
\includegraphics[width=\figurewidth]{mixtures_vs_K_luv}
\caption{Comparisons of approximations.  \textsl{top-left:} The
  dependence of amplitude $a^{\exp}_m$ and root-variance
  $\sqrt{v^{\exp}_m}$ on $M^{\exp}$ for the exp profile.
  \textsl{top-right:} The same but for the dev profile.
  \textsl{bottom-left:} The same but for the lux profile.
  \textsl{bottom-right:} The same but for the luv profile.\label{fig:M}}
\end{figure}
